Type Refinements for the Working Class

### 2015-11-22 paper.tex
Restore rule-style definition of functional refinement
typos

\begin{quote}
  To know $\HEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M,N}{\Exprs_\sigma(\Upsilon')}$, that from
  $\HRMemEq{\Upsilon}{\Psi\rho}{M}{N}{\chi\rho}$, you can conclude
  $\HRMemEq{\Upsilon}{\Psi\rho}{\Subst{M}{x}{\phi\rho}}{\Subst{N}{x}{\psi\rho}}{\tau}$.

\end{quote}

>>>>

\begin{quote}
  To know $\HEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}$ is to know, for any renaming
  \begin{tikzcd}[cramped]
    \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
  \end{tikzcd}
  and closed terms $\Member{M,N}{\Exprs_\sigma(\Upsilon')}$, that from
  $\HRMemEq{\Upsilon}{\Psi\rho}{M}{N}{\chi\rho}$, you can conclude
  $\HEqRefines{\Upsilon}{\Psi\rho}{\Subst{M}{x}{\phi\rho}}{\Subst{N}{x}{\psi\rho}}{\tau}$.
  In other words:
  %
  \[
    \infer[\PFunRefSnoc]{
      \HEqRefines{\Upsilon}{\Psi,x:\chi}{\phi}{\psi}{\tau}
    }{
      \begin{array}{l}
        \forall
        \begin{tikzcd}[cramped, ampersand replacement = \&]
          \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
        \end{tikzcd}.\
        \forall \Member{M,N}{\Exprs_\sigma(\Upsilon')}.\\
        \left(\HRMemEq{\Upsilon}{\Psi\rho}{M}{N}{\chi\rho}\right)
        \Rightarrow
        \left(\HEqRefines{\Upsilon}{\Psi\rho}{\Subst{M}{x}{\phi\rho}}{\Subst{N}{x}{\psi\rho}}{\tau}\right)
      \end{array}
    }
  \]
\end{quote}
